The Heavy Photon Search Test Detector

### 2014-04-02 hps-testrun-nim.tex
Edit from John.

\begin{abstract}
Construction and design of the Heavy Photon Search (HPS) experiment, designed to search for an 
\ee resonance from heavy photon production in a fixed-target setup at the Thomas Jefferson 
Accelerator Facility (JLab), is ongoing. As a first stage, a test apparatus was constructed and 
operated at JLab to demonstrate that the apparatus and data acquisition systems are technically 
feasible and that the trigger rates and occupancies encountered in electron-beam running are as 
simulated. Given dedicated running time with electron beams, the HPS Test apparatus is 
capable of searching for heavy photons in unexplored regions of parameter space.  Charged 
particle tracks are measured with a compact forward silicon microstrip detector and 
electromagnetic showers from electrons and photons are detected in a dense array of 
PbWO$_{4}$ crystals. To allow clean passage of the scattered intense electron beam after 
the thin tungsten target foil while keeping sensitivity to low-mass heavy photons,  the sensitive region 
of the detectors are place at $\pm 15$~mrad with respect to the horizontal beam plane. 
The discrimination between prompt and displaced \ee pairs requires the first layer of silicon 
sensors to be placed only 10~cm behind the target and 0.5~mm from the beam. 
The HPS Test apparatus included the high-speed trigger and data acquisition needed for 
running with electron beams. Details of the layout and performance of the Test detectors and 
associated readout electronics are presented. 
\end{abstract}

@@

%% main text
\section{Introduction}
\label{introduction}
Heavy photons, aka "hidden sector" or "dark" photons, or from here on \Aprime{}, are particles with 
mass $10-1000$~MeV 
which couple weakly to the Standard Model photon~\cite{Holdom:1985ag}, so can be radiated by 
electrons, and can decay 
into \ee pairs, albeit at rates far below those of QED trident processes. They have been suggested by 
numerous Beyond Standard Model theories and as an explanation of the current muonic $g-2$ 
anomaly, and may couple directly to hidden sector particles that may constitute all or some of the 
dark matter~\cite{ArkaniHamed:2008qn}. 
Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
suggests that \Aprime's couple to electric charge with strength $\epsilon$e, where 
$\epsilon$ is in the range of $10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes 
\Aprime{} searches viable in moderate energy fixed target 
electroproduction~\cite{Bjorken:2009mm}, but require large data sets and good mass resolution
to identify a small mass peak above the copious QED background at very small production 
angles. At small couplings, \Aprime's become long-lived, so detection of a displaced decay 
vertex can reject the prompt QED background and boost experimental sensitivity.

The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and 
vertex signatures by placing a $\approx 1$~m long silicon tracking and vertexing detector 10~cm 
downstream  of a 0.25\%~$\chi_0$ tungsten target inside a dipole magnet. The experiment runs at high 
rates (up to 50kHz), exploiting the 
100\% duty cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to 
accumulate the need statistics. The trigger is provided by a fast electromagnetic calorimeter just 
downstream of the tracking detector.

The HPS Test apparatus, a simplified version of the HPS experiment, was proposed and 
approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of HPS. 
Its purposes included demonstrating that the apparatus and data acquisition systems are 
technically feasible and that the trigger rates and occupancies encountered in electron-beam 
running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
The stringent constraints on the detector requirements therefore also applied to the Test detector:
\begin{itemize}
\item large and uniform acceptance in the forward region close to the beam in order to catch boosted 
\Aprime{} decay products,
\item beam passage through the apparatus in vacuum, to eliminate direct interactions with the 
detector and minimize beam gas interactions, 
\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
50~kHz,
\item excellent track reconstruction efficiency for electrons and positrons,
\item good angular and momentum resolution to reconstruct invariant mass precisely,
\item excellent vertex resolution to discriminate displaced \Aprime{} decays from prompt QED 
backgrounds,
\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
\item data handling rates of 100~MB/s to permanent storage,
\item detector components that can survive and efficiently operate in a high radiation environment 
with local doses exceeding $100$~Mrad.
\end{itemize}

The Test apparatus was installed on April 19, 2012, and ran parasitically with the HDice 
experiment~\cite{HDice}, using its photon beam, until May 18. The JLab run schedule 
precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
valuable dedicated run with the photon beam. Most technologies used in the Test apparatus will 
be used in the HPS detector with some improvements to each of the systems; both from lessons 
learned during running of the Test run but also from less schedule and budget constraints.

@@

%Of particular importance, data from the dedicated photon beam running has been used to 
%compare the measured trigger rates with those expected in simulation. The Test Run trigger rate is 
%almost entirely due to photons which have converted to \ee pairs in a thin target upstream of HPS 
%and it 
%is sensitive to their multiple Coulomb scattering in the conversion target.  During electron beam 
%running, 
%the tails of the multiply Coulomb scattered primary beam are the dominant source of occupancy in %the 
%tracker and trigger rate in the electromagnetic calorimeter. 
%The trigger rates in the Test Run are also sensitive to the tails of the multiple Coulomb
%scattering distribution. Good agreement between the measured and simulated rates confirms
%our understanding of multiple Coulomb scattering and 
%the reliability of the background simulation used to benchmark the physics reach of the HPS 
%experiment.

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at an energy of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam and the degraded electrons after the target are spread out horizontally by 
the analyzing magnet constitute a "dead zone" which must be completely avoided. The apparatus is 
split vertically $15$~mrad above and below the beam plane and the beam is transported in vacuum 
to minimize beam-gas interaction backgrounds. Even so, background occupancy in the detectors 
remain high and are dominated by the degraded primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger comes from a PbWO$_{4}$ crystal calorimeter. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

The silicon tracking and vertexing detector for HPS Test, or SVT, operates in an existing vacuum 
chamber inside the pair spectrometer analyzing magnet in Hall B at JLab.  There are five 
measurement stations, or ``layers,'' placed immediately downstream of the target. Each layer 
comprises a pair of closely-spaced silicon microstrip sensors responsible for measuring a single 
coordinate, or ``view.'' Introduction of a small (50 or 100~mrad) stereo angle between the two 
sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
of the detector with one redundant layer. Each layer In order to accommodate the dead zone, the 
SVT is built in two halves that are mirror reflections of one another about the plane of the nominal 
electron beam.  Each layer in one half are supported on a common support plate with independent 
cooling and readout.

Each half of the electromagnetic calorimeter, or ECal, consists of 221 PbWO$_4$ crystals arranged 
in rectangular formation. There are five rows with 46 modules in each row except the row closest to 
the beam plane which has 37. The light from each crystal 
is read out by Avalanche Photodiode (APD) glued on the back surface of the crystal. 
Signals from the APDs were amplified using custom-made amplifier boards before being sent to the 
readout electronics.

@@

For the duration of the Test run all SVT modules and APV25 chips were configured to their 
nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
sensors were operated within a temperature range of  $20-24^\circ$C.
Approximately 97\% of the 12,780 SVT channels were found to
be operating normally;  the fraction of dead or noisy channels varied from 2.4\% to 4.7\% throughout 
the Test run. Most of these were due to 2-4 misconfigured APV25 ASICs, a known noisy 
half-module and a couple of known APV25 ASICs.

@@

After a trigger is received, six samples of the corresponding output of the APV25 ASIC shaper circuit are 
digitized. The six pedestal-subtracted samples from every channel in the SVT are the basis for offline hit 
reconstruction. The typical pulse shape obtained shown in Fig.~\ref{fig:pulse_shape} also 
demonstrates that the SVT was well timed in to the trigger with the rise of the pulse at the 3rd sampling 
point.
\begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/run1351_110513_samples_L1_top.pdf}
	\caption{Accumulation of six pedestal-subtracted samples from individual SVT channels associated 
	with hits on tracks.}
	\label{fig:pulse_shape}
}
\end{center}
\end{figure}
These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
strips with the position of a cluster on the sensor determined by the amplitude-weighted mean.
With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
the characteristic Landau shape. 
%, see Fig.~\ref{fig:cluster_pulse}.  
A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
runs giving a signal to noise ratio of $21-25$. Lab-based radioactive source tests was used to 
provide the absolute charge normalization.
%\begin{figure}[]
%\begin{center}
%{\small
%	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
%	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
%    	\caption{ The cluster charge distribution for hits associated with a track. }
%	\label{fig:cluster_pulse}
%}
%\end{center}
%\end{figure}

In order to find the time and amplitude of each hit, $t_0$,  the six samples from each channel are fitted to 
an ideal $CR-RC$ function. After clustering hits on a sensor, the hit time for each cluster is computed as 
the amplitude-weighted average of the individually fitted $t_0$ on each channel. The $t_0$-resolution is 
studied by comparing the cluster hit time with the average of all cluster hit times on the track, 
see Fig.~\ref{fig:tracktime}, which has the expected jitter due to clock phase and trigger, 
approximately 25~ns. 
\begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=7cm]{figures/test_run_1351_hit_time_corrected_top_layer2_mod.pdf}
	\caption{
	The residual of individual cluster times with the average of all clusters on the track. }
	\label{fig:tracktime}
}
\end{center}
\end{figure}
After correcting for offsets from each sensor (time-of-flight, clock phase) and accounting for the 
correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is somewhat 
worse than the approximately 2~ns resolution expected for S/N~25 which we attribute to the true 
pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
APV25 ASIC pulse shaping time will also improve time resolution. 
These results show that we can operate with the six sample readout mode of the APV25 chip and 
achieve time resolution adequate for pileup rejection during electron running in HPS.

>>>>

\begin{abstract}
The  Heavy Photon Search (HPS), an experiment to search for a hidden sector photon in fixed target 
electroproduction, is preparing for installation at the Thomas Jefferson National Accelerator Facility 
(JLab) in the Fall of 2014.  As the first stage of this project, the HPS Test run apparatus was 
constructed and operated in 2012 to demonstrate the experiment's technical feasibility and to  confirm 
that the trigger rates and occupancies are as expected. This paper describes the Test Run apparatus 
and readout electronics and its performance. In this setting, a heavy photon can be identified as a 
narrow\ee  mass peak above the trident background or as a decay vertex displaced from
the production target, so charged particle tracking and vertexing are needed for its detection. In the 
HPS Test run, charged particles are measured
with a compact forward silicon microstrip vertex/tracker inside a dipole magnet. Electromagnetic 
showers are detected in a PbW0$_{4}$ 
crystal calorimeter situated behind the magnet used to trigger the experiment and identify 
electrons and positrons. Both detectors are placed close to the 
beam line and split top-bottom. This arrangement  provides sensitivity to low-mass heavy photons,  
allows clear  passage of the unscattered beam, 
and avoids the spray of degraded electrons coming from the target. 
The discrimination between prompt and displaced \ee pairs requires the first layer of silicon 
sensors be placed only 10~cm downstream of the target. The expected signal is small, and the 
trident background huge, so the experiment requires very large statistics. Accordingly, the
HPS Test run utilizes  high-rate readout and data acquisition electronics and a fast trigger to
perfectly exploit the essentially 100\% duty cycle of the CEBAF accelerator.
\end{abstract}

@@

%% main text
\section{Introduction}
\label{introduction}
The heavy photon (\Aprime{}), aka a "hidden sector" or "dark" photon, is a particle with mass 
$10-1000$~MeV which couples weakly to electric charge by mixing with the Standard Model 
photon~\cite{Holdom:1985ag}. Consequently, it can be radiated by electrons and subsequently decay 
into \ee pairs, albeit at rates far below those of QED trident processes. Heavy photons have been 
suggested by numerous Beyond Standard Model theories `\cite{Essig:2013lka}, to explain the 
discrepancy 
between theory and experiment of the muon's $g-2$ ~\cite{Pospelov:2008zw}, and as a possible 
explanation of recent astrophysical anomalies.  Heavy photons  couple directly to  hidden sector 
particles with "dark" or "hidden sector" charge; these particles
could constitute all or some of the dark matter~\cite{ArkaniHamed:2008qn}. 
Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
suggests that  the coupling to electric charge, $\epsilon$e, has $\epsilon$ in the range of 
$10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes \Aprime{} searches viable in 
medium energy fixed target electroproduction~\cite{Bjorken:2009mm}, but requires large data sets and 
good mass resolution to identify a small mass peak above the copious QED background. At small 
couplings, \Aprime's become long-lived, so detection of a displaced decay vertex can reject the prompt 
QED background and boost experimental sensitivity.

The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and secondary
vertex signatures to search for A's. It uses  a $\approx 1$~m long silicon tracking and vertexing detector
inside a dipole magnet to measure charged particle trajectories and a fast electromagnetic calorimeter 
just downstream of the magnet to provide a trigger and identify electrons. The experiment utilizes very 
high rate front end electronics and runs at high trigger rates (up to 50kHz), exploiting the 100\% duty 
cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to accumulate 
the needed statistics.

The HPS Test apparatus, a simplified version of the HPS experiment, was proposed and 
approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of HPS. 
Its purposes included demonstrating that the apparatus and data acquisition systems are 
technically feasible and  the trigger rates and occupancies to be  encountered in electron-beam 
running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
The key design criteria for HPS and the HPS Test Run are the same:
\begin{itemize}
\item large and uniform acceptance in the forward region close to the beam in order to catch boosted 
\Aprime{} decay products,
\item beam passage through the apparatus in vacuum, to eliminate direct interactions with the 
detector and minimize beam gas interactions, 
\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
50~kHz,
\item excellent track reconstruction efficiency for electrons and positrons,
\item good angular and momentum resolution to reconstruct invariant mass precisely,
\item excellent vertex resolution to discriminate displaced \Aprime{} decays from prompt QED 
backgrounds,
\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
\item data handling rates of 100~MB/s to permanent storage,
\item detector components that can survive and efficiently operate in a high radiation environment 
with local doses exceeding $100$~Mrad.
\end{itemize}

The Test apparatus was installed on April 19, 2012, and ran parasitically in the photon beam of the HDice 
experiment~\cite{HDice} until May 18. The JLab run schedule 
precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
valuable dedicated run at the end of scheduled CEBAF running. This final running provided
enough data to demonstrate the functionality of the apparatus, document its performance, and
explore trigger rates, as shown below. 
This paper reviews the HPS Test apparatus; documents the performance of the trigger, 
data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
in calculating the physics reach of the HPS experiment.

@@

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at an energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in a final state particle within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
which have radiated in the target disperse horizontally in the field of the analyzing magnet. Together 
they constitute a "wall of flame" which must be completely avoided. Accordingly, 
the apparatus is split vertically to avoid a "dead zone", the region within $\pm 15$~mrad of the beam 
plane. In addition, the beam is transported in vacuum through the tracker to minimize beam-gas 
interaction backgrounds. Even with these precautions, the occupancies of sensors near the beam 
plane are high, dominated by the
multiple Coulomb scattering of the primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
The trigger comes from a highly-segmented  PbWO$_{4}$ crystal calorimeter located just downstream 
of the dipole magnet. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

The silicon tracking and vertexing detector for HPS Test, or SVT, resides in a vacuum 
chamber inside the pair spectrometer analyzing magnet in Hall B at JLab. The SVT has five 
measurement stations, or ``layers,'' beginning10 cm downstream of the target. Each layer 
comprises a pair of closely-spaced silicon microstrip sensors responsible for measuring a single 
coordinate, or ``view.'' Introduction of a small (50 or 100~mrad) stereo angle between the two 
sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
of the detecto. In order to accommodate the dead zone, the 
SVT is built in two halves that are approximately mirror reflections of one another about the plane of the 
nominal electron beam.  Each layer in one half is supported on a common support plate with 
independent cooling and readout.

The electomagnetic calorimeter (ECal) is also split into two halves. Each half of the ECal consists of 
221 PbWO$_4$ crystals arranged in rectangular formation. There are five rows with 46 modules in 
each row except the row closest to the beam plane which has 37. The light from each crystal 
is read out by an Avalanche Photodiode (APD) glued on the back surface of the crystal. 
Signals from the APDs are amplified using custom-made amplifier boards before being sent to the 
data acquisition electronics.

@@

For the duration of the Test run all SVT modules and APV25 chips were configured to their 
nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
sensors were operated within a temperature range of  $20-24^\circ$C.
Approximately 97\% of the 12,780 SVT channels were found to
be operating normally;  the fraction of dead or noisy channels varied from 2.4\% to 4.7\% throughout 
the Test run. Most of these losses were due to 2-4 misconfigured APV25 ASICs, a known noisy 
half-module and problems in two particular APV25 ASICs.

@@

After a trigger is received, the amplitude  of every  APV25 analoge output  is sampled and digitized in 
six consecutive time bins, separated by roughly 25~ns.  
The typical pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape}. As the figure demonstrates,  
the SVT was well timed-in to the trigger with the rise of the pulse at the 3rd sampling 
point.
\begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/run1351_110513_samples_L1_top.pdf}
	\caption{Accumulation of six pedestal-subtracted samples from individual SVT channels associated 
	with hits on tracks.}
	\label{fig:pulse_shape}
}
\end{center}
\end{figure}
These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
strips with the position of a cluster on the sensor determined by the amplitude-weighted mean.
With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
the characteristic Landau shape. 
%, see Fig.~\ref{fig:cluster_pulse}.  
A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
runs giving a signal to noise ratio of $21-25$. Lab-based radioactive source tests was used to 
provide the absolute charge normalization.
%\begin{figure}[]
%\begin{center}
%{\small
%	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
%	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
%    	\caption{ The cluster charge distribution for hits associated with a track. }
%	\label{fig:cluster_pulse}
%}
%\end{center}
%\end{figure}

In order to find the time, $t_0$, and amplitude of each hit, the six samples from each channel are fitted 
to an ideal $CR-RC$ function. After clustering hits on a sensor, the hit time for each cluster is computed 
as the amplitude-weighted average of the individually fitted $t_0$ on each channel. The 
$t_0$-resolution is studied by comparing the cluster hit time with the average of all cluster hit times on 
the track, see Fig.~\ref{fig:tracktime}, which has the expected jitter due to clock phase and trigger, 
approximately 25~ns. 
\begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=7cm]{figures/test_run_1351_hit_time_corrected_top_layer2_mod.pdf}
	\caption{
	The residual of individual cluster times with the average of all clusters on the track. }
	\label{fig:tracktime}
}
\end{center}
\end{figure}
After correcting for offsets from each sensor (time-of-flight, clock phase) and accounting for the 
correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is somewhat 
worse than the approximately 2~ns resolution expected for S/N~25 which we attribute to the true 
pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
APV25 ASIC pulse shaping time will also improve time resolution. 
These results show that we can operate with the six sample readout mode of the APV25 chip and 
achieve time resolution adequate for pileup rejection during electron running in HPS.
